\begin{acknowledgements}
All praise and gratitude writer are turning to the presence of God Almighty because with His bounties and blessings I can finish first Internship report titled "Analysis of EEG Against Drug Users Using WAVELET Method" which is one of the requirements to continue the learning process to the next level. 
\par
In writing this, I Internship report writers face many obstacles, one of which is the difficulty in obtaining data and information as well as the limitations of the knowledge possessed by the author. However, the authors attempted with the capabilities to complete this report.
\par
For that on this occasion the author would like to thank:

\begin{enumerate}
    \item To Parents, Brothers, and All my friends who have supported both regarding morale to the material.
    \item Both my parents and family have encouraged and encouraged me.
    \item Rolly Maulana Awangga, ST, MT as lecturers on campus and in the Internship which has provided guidance as well as ease of analysis and preparation of reports.
    \item All those who have contributed to the completion of this first Internship report.
    \item Syafrial Fachri Pane, S.T., M.T.I. As the Companion Examiner for this Internship I stage.
    \item Roni Andarsyah. S.T., M.Kom. As Internship I Coordinator for Academic Year 2018/2019.
    \item M. Yusril Helmi Setyawan, S.Kom., M.Kom. As Chair of the 2018/2019 DIV Informatics Engineering Study Program.
    \end{enumerate}
\par
The author realized that writing this report is far from perfect, therefore, criticism and constructive suggestions are needed by the author to work more leverage for the future. 
\par
End the authors hope that this report can be useful and add a better insight to the reader. 

\par
\begin{raggedleft}
Bandung, december 11, 2018

\end{raggedleft}


\end{acknowledgements}

