\chapter{Discussion}

\par
       Methadone is a type of synthetic opioid drug, used as an analgesic and for treating addiction from users of the opioid group, such as heroin, morphine, and codeine. But improper use can also have a negative impact on health. Although methadone is very necessary for medical care and services, especially drug addicts, if it is misused or used is not in accordance with the standard of care, especially if accompanied by illicit circulation, it will have a very detrimental effect on individuals or society, Electroencephalogram (EEG) is an activity to record the electrical activity of brain neurons. Using EEG, the condition of relaxing or not drug users can be observed. EEG signals are widely used to detect brain disorders in the world of health. However, EEG signals are not made to be ready to detect brain abnormalities automatically. Therefore, the characteristics of the EEG signal are safe.Simultaneous EEG modulation of the volume of BOLD activity from the target brain region and investigation of electrophysiological activity related to the results of objects using illegal drugs will show human brain waves.
    
\par
    The conclusions obtained in this research method are where the researcher determinesthe method used to process the data from the object determined by the research willdetermine the quality of the research.  In this step the researcher can find out more, byobserving, reading the literature identifying one predetermined aspect with relevantenvironmental (drug users) relevan.
    
\par
    In this study, eeg signals that have been recorded using WINEEG and analysis usingWAVELET can be concluded that the condition of the otas of the person being studiedcan be observed.  Observations made by comparing the results of the subject’s braindata record before and after being given a stimulus.  This analysis also shows largevariations due to drugs or methadone.  Therefore, the use of the proposed method, theassessment of the brain condition of drug users using WAVELET, the brain conditionof drug users and the identification of efficient EEG signals can help in research