\chapter{Introduction}
\section{Background}
Drug broadcasting among youth and teenagers cannot be denied and still consume it in the environment around us. It seems to be for health and a little future. \cite{wagner2016using}
\par
The danger of drugs for addicts and adolescents, students is very much and if not immediately spent on buying drugs then drug use will overdose and one of the factors that can be felt from drug use can damage the mental and cure the tragic. \cite{warnock2018life}
\par
The effect parameters derived from quantitative EEG analysis seem to be very suitable for marking relationships between nakoba users or not drug users. EEG parameters represent many characteristics of pharmacodynamic actions that are ideal, sustainable, and objective These features provide an opportunity to find out the relationship between the effects for drugs on individuals, which makes valuable information about brain waves of drug users.\cite{mandema1992electroencephalogram}
\par
 Electroencephalogram (EEG) is an activity to record the electrical activity of brain neurons. EEG is being used.\cite{hanley2017brain} Using EEG, the condition of relaxing or not drug users can be observed. EEG signals are widely used to detect brain disorders in the world of health. However, EEG signals are not made to be ready to detect brain abnormalities automatically. Therefore, the characteristics of the EEG signal are safe.\cite{zotev2018real} Simultaneous EEG modulation of the volume of BOLD activity from the target brain region and investigation of electrophysiological activities related to the results of objects using illegal drugs will show human brain waves.\cite{chiang2017dangers} electroencephalography (EEG), we investigated and compared reciprocal accuracy and efficiency and direct EEG forward approaches for brain electrical current sources based on existing methods, adjoint (AA) approaches and partial integration approaches in relation to the concept of data transfer matrices. By analyzing numerical results, comparing with EEG's advanced potential is derived analytically and estimates complexity. \cite{palva2018ghost}, and to overcome the effects of linear sources attached to standard interaction steps, alternative phases and connectivity steps based on amplitude correlations, such as imaginary coherence and orthogonal amplitude correlations proposed. Defined to be insensitive to zero-lag correlation, this technique has become increasingly popular in the identification of correlations that cannot be attributed to field spread or volume conduction. This fundamental problem is region-based analysis and importance-for-all mapping. Most importantly, beyond defining and describing the problem of false interactions, we provide strict quantification of these effects through extensive simulations. In addition, we further demonstrated that the mixing signal also limits the separation of the neuron phase and amplitude correlation
 \par
 Methadone is a type of synthetic opioid drug, used as an analgesic and for treating addiction from users of the opioid group, such as heroin, morphine, and codeine. But its improper use can also have a negative impact on health. Although methadone is indispensable for medical treatment and services, especially drug addicts, if it is misused or used is not by the standard of treatment, especially if accompanied by illicit circulation, it will have a very detrimental e ect on individuals or society ,especially the younger generation. \cite{lim2015analysis} Detection of the use of methadone and other types of drugs is quite a lot done in government agencies, hospitals, and industries to screen employees/workers who will carry out medical tests. Already many methods used are detection using urine, using saliva or doing screening by doing brain signal recording. \cite{jin2015p300}
\section{Problems Identification}
Identify the problem based on the background are:
\begin{enumerate}
    \item How the human brain wave monitor for drug users
\end{enumerate}

\section{Objective and Contribution}
\subsection{Objective}
\begin{enumerate}
    \item Monitoring the human brain waves against drug users
\end{enumerate}
\subsection{Contributione}
\begin{enumerate}
    \item Help monitor brain waves to drug users and the detection of EEG signals
\end{enumerate}
\section{Scoop and Environtment}
The scope of the study conducted by researchers are:
\begin{enumerate}
    \item Showing graph EEG
    \item Real-Time Monitoring brain waves and determine the characteristics based  on the EEG signals. 
\end{enumerate}